---
title: "Homework 2"
author: "Christine Hou"
date: "2022-10-11"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Github link: https://github.com/christinehou/STAT433-HW2

```{r,comment=NA}
library(tidyverse)
library(nycflights13)
library(dbplyr)
```


## Section I: What time of day should you fly if you want to avoid delays as much as possible? 

```{r,comment=NA}
flights %>% filter (dep_delay > 0) %>% 
  group_by(hour) %>%
  summarize(avg_delay = mean(dep_delay)) %>%
  arrange(avg_delay)
```

> I choose the average of `dep_delay` as the standard (different from class notes, but i want to try another method). Generally, I filter the rows with positive `dep_delay` and group by `hour`, then calculate the average delay time named `avg_delay` to see the minimum value. It's clear that the `avg_delay = 15.3` is the shortest when `hour = 5`, so the best choice to avoid delay time should be at 5am every day.  

## Section II - What did the choice depend on?

> In this section, I would like to explore three aspects: `carrier_n    `,`plane_n`, and `visib`. I use scatter plot with connected lines to see the overall distribution and change over time. The x-axis is the hour in one day, and y-axis is changed based on my interest in each part. According to the analysis, it's clear to see that my three interests all have some impacts on how I choose the time to take flights for less delay. At 5am, all airports tend to have less carriers, less total plane counts, and better visibility, so the flights tend to be on time and people will have shorter delay time so that we can avoid delay as much as possible.

#### Pattern 1 - Carrier Count

> In the first part, I explore how many types of carrier entering the airport, which is using `n_distinct` to avoid repeated carrier but only count distinct type. Then, the plot gives a very good explanations or support that 5am is a good time because we have less carrier entering the airport, so the airport is not very crowded. The plot also shows that around late night there tends to have carrier counts less than 5, but it is reasonable because the carriers need to leave the airport to final destination, and they cannot stay overnight, but the late night `dep_delay` is much higher, so still 5am is the best choice, and the choice does depend on carrier count.

```{r,comment=NA}
carrier_n = flights %>%
  filter(!is.na(dep_delay)) %>%
  select(hour,carrier) %>%
  group_by(hour) %>%
  summarize(count = n_distinct(carrier))

head(carrier_n, 10)

carrier_n %>%
  ggplot(aes(x = hour, y = count))+
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 5,color = 'red') +
  geom_vline(xintercept = 5,color = ' blue')
```

#### Pattern 2 - Flight Count

> In the second part, I explore how the number of planes `count` influence the delay time `dep_delay`. I prefer to see the general patter, like how the overall plane counts can influence, not specific airline. Therefore, based on the plots, it's clear to see that the number of flights entering the airport is increasing since 5am. This conclusion is reasonable because when the airports receive more flights in one hour, the airport needs more time to keep the order and resolve more emergencies.

```{r,comment=NA}
plane_n = flights %>%
  select(hour,dep_delay, tailnum) %>%
  filter(!is.na(dep_delay)) %>%
  group_by(hour) %>%
  summarize(count = n())

head(plane_n, 10)

plane_n %>%
  ggplot(aes(x = hour, y = count))+
  geom_point() +
  geom_line() + 
  geom_hline(yintercept = 1944,color = 'red') +
  geom_vline(xintercept = 5,color = ' blue')
```

#### Pattern 3 - Visibility

> In the third part, I explore how the weather, specifically the visibility, influence the `dep_delay`. I join`visib` column in `weather` data set to `flights` data set such that we can see, filter, and mutate the values together in one single data set. I use `avg_visib` as main standard, which is the average of visibility in each hour, and for calculation convinience, I replace any `NA` value in `visib` column to `0`. Through the plot, we can see that the visibility is relatively high (`avg_visib = 9.19`). Even though it is not the highest because `hour = 5` is still the early morning, which can be a reason influencing the visibility, I still think 5am is the best choice and `visib` can be a factor but not very strong.

```{r,comment=NA}
visib = flights %>% 
  left_join(weather, by = c('year','month','day','hour','origin')) %>%
  gather(key = 'condition', value = 'value', visib) %>%
  filter(!is.na(dep_delay)) %>%
  select(hour, value, dep_delay) %>%
  mutate(value = ifelse(is.na(value),0,value)) %>%
  group_by(hour) %>%
  summarize(avg_visib = mean(value))

head(visib, 10)

visib %>%
  ggplot(mapping = aes(x = hour, y = avg_visib)) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 9.19,color = 'red') +
  geom_vline(xintercept = 5,color = ' blue')
```
